\Large \bf Module-aware Fracture and Recombination for Dynamic Analysis

### 2019-12-10 paper/draft.tex
Update stuff

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Formatting Submissions for a USENIX Conference:\\
  An (Incomplete) Example}

@@

Intro

@@

\bibliographystyle{plain}
\bibliography{\jobname}

>>>>

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Module-aware Fracture and Recombination for Dynamic Analysis}

@@

Some citations to ensure we can see them~\cite{Christophe:2015:DAU:2819009.2819180, Keil:2013:EDA:2508168.2508176, Lehmann:2019:WFD:3297858.3304068, Sun:2018:EDA:3178372.3179527}.

@@

\bibliographystyle{plain}
\bibliography{bib}
